Plot local false sign rate results

### 2016-10-14 analysis/IPvsEM.Rmd
Encountered error in running 'ash' with REBayes package using stephens999/ashr with 'general' branch.

@@

The following simulation assumes $\beta \sim N(0,betasd^2)$ and with $\hat{\beta}$ having standard deviation 1.
```{r}
timed_sims = function(ash.args,nsim=20,nmin = 100,nmax = 1000,betasd=1){
  n=10^seq(log10(nmin),log10(nmax),length=nsim)
  elapsed.time= rep(0,nsim)
  for(i in 1:nsim){
    set.seed(i)
    betahat = rnorm(n[i],sd=sqrt(1+betasd^2))
    elapsed.time[i] = system.time(do.call(ashr::ash,args = modifyList(ash.args,list(betahat = betahat, sebetahat=1))))[3]
  }
  return(data.frame(elapsed.time=elapsed.time,seed=1:nsim,n = n))
}
```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

@@

The following simulation assumes $\beta \sim N(0,\sigma_{\sf betasd}^2)$ and
with $\hat{\beta}$ having standard deviation 1.

```{r generate_data}
timed_sims = function(ash.args,nsim = 20,nmin = 100,nmax = 1000,betasd = 1){
  n=10^seq(log10(nmin),log10(nmax),length=nsim)
  elapsed.time= rep(0,nsim)
  for(i in 1:nsim){
    set.seed(i)
    betahat = rnorm(n[i],sd=sqrt(1+betasd^2))
    elapsed.time[i] = system.time(do.call(ashr::ash,args = modifyList(ash.args,list(betahat = betahat, sebetahat=1))))[3]
  }
  return(data.frame(elapsed.time=elapsed.time,seed=1:nsim,n = n))
}
```

### 2016-10-14 analysis/adaptive_shrinkage.Rmd
Encountered error in running 'ash' with REBayes package using stephens999/ashr with 'general' branch.

```{r plot_lfsr}

z_lfsr_plot = function(df,ylab = "Observed Z score",xlab = "lfsr")
  ggplot(df,aes(x = lfsr,y = betahat/s,color = 1/s)) +
    xlab(xlab) + ylab(ylab) + geom_point() + facet_grid(.~scenario) +
    scale_colour_gradient2(midpoint = median(1/s),low = "blue",
                           mid = "white",high = "red",space = "Lab")

@@

Session information.

>>>>

```{r plot_lfsr}
z_lfsr_plot = function(df,ylab = "Observed Z score",xlab = "lfsr")
  ggplot(df,aes(x = lfsr,y = betahat/s,color = 1/s)) +
    xlab(xlab) + ylab(ylab) + geom_point() + facet_grid(.~scenario) +
    scale_colour_gradient2(midpoint = median(1/s),low = "blue",
                           mid = "white",high = "red",space = "Lab")

@@

## Session information.

### 2016-10-14 analysis/efron.fcr.Rmd
Encountered error in running 'ash' with REBayes package using stephens999/ashr with 'general' branch.

We can also run ash with the "true" g, to allow us to compare the lfsr, lfdr etc. 
```{r}
  true.g = ashr::normalmix(c(0.9,0.1),c(0,-3),c(0,1))
  res.ash.true = ashr::ash(z,1,g=true.g,fixg=TRUE)
```

@@

We can also run qvalue and locfdr. We see that locfdr perhaps performs a bit better than ash for the decomposition here, but the estimated local fdrs are pretty similar. Here qvalue does less well because of the asymmetry which we didn't take account of.
```{r}
library(qvalue)
library(locfdr)
res.locfdr = locfdr(z,nulltype = 0)
res.qvalue = qvalue(p=pchisq(z^2,df=1,lower.tail = FALSE))  
#res.pos.qvalue = qvalue(p=pchisq(z[z>0]^2,df=1,lower.tail = FALSE))  
#res.neg.qvalue = qvalue(p=pchisq(z[z<0]^2,df=1,lower.tail = FALSE))  
#df1= data.frame(Truth = res.ash.true$lfdr,Estimate=res.locfdr$fdr,Method="locfdr")
#df2= data.frame(Truth = res.ash.true$lfdr,Estimate=res.ash$lfdr,Method="ash.hu")
#df3 =data.frame(Truth = res.ash.true$lfdr,Estimate=res.qvalue$lfdr,Method="qvalue")
#df4 =data.frame(Truth = res.ash.true$lfdr[z<0],Estimate=res.neg.qvalue$lfdr,Method="qvalue (-)")
#df5 =data.frame(Truth = res.ash.true$lfdr[z>0],Estimate=res.pos.qvalue$lfdr,Method="qvalue (+)")

>>>>

We can also run ash with the "true" g, to allow us to compare the lfsr, lfdr etc.
```{r}
  true.g = ashr::normalmix(c(0.9,0.1),c(0,-3),c(0,1))
  res.ash.true = ashr::ash(z,1,g=true.g,fixg = TRUE)
```

@@

We can also run qvalue and locfdr. We see that locfdr perhaps performs a bit better than ash for the decomposition here, but the estimated local fdrs are pretty similar. Here qvalue does less well because of the asymmetry which we didn't take account of.
```{r}
library(qvalue)
library(locfdr)
res.locfdr = locfdr(z,nulltype = 0)
res.qvalue = qvalue(p = pchisq(z^2,df=1,lower.tail = FALSE))
#res.pos.qvalue = qvalue(p=pchisq(z[z>0]^2,df=1,lower.tail = FALSE))
#res.neg.qvalue = qvalue(p=pchisq(z[z<0]^2,df=1,lower.tail = FALSE))
#df1= data.frame(Truth = res.ash.true$lfdr,Estimate=res.locfdr$fdr,Method="locfdr")
#df2= data.frame(Truth = res.ash.true$lfdr,Estimate=res.ash$lfdr,Method="ash.hu")
#df3 =data.frame(Truth = res.ash.true$lfdr,Estimate=res.qvalue$lfdr,Method="qvalue")
#df4 =data.frame(Truth = res.ash.true$lfdr[z<0],Estimate=res.neg.qvalue$lfdr,Method="qvalue (-)")
#df5 =data.frame(Truth = res.ash.true$lfdr[z>0],Estimate=res.pos.qvalue$lfdr,Method="qvalue (+)")

### 2016-10-14 analysis/estimate_mode.Rmd
Encountered error in running 'ash' with REBayes package using stephens999/ashr with 'general' branch.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

@@

I conjecture that the mean of the posterior means should be close to the optimum for the mode...
maybe even equal to it. (That is, this would constitute a fixed point for the update. We aren't
explicitly using that directly in the current implementation; the uniform mixture uses optim to
do it numerically; the normal mixture uses a true EM I think...)

```{r}
library(ashr)
check_mode = function(betahat, sebetahat,mixcompdist){
    z.ash=ash(betahat,sebetahat,mixcompdist=mixcompdist,mode="estimate")
    average.posteriormean = mean(get_pm(z.ash))
    fitted.mode = comp_mean(get_fitted_g(z.ash))[1]

    z.ash1 = ash(betahat-fitted.mode,sebetahat, mixcompdist=mixcompdist) #refit to get g
    g = get_fitted_g(z.ash1)
    loglik = get_loglik(z.ash1)

    loglik.down = ash(z-fitted.mode-0.01,1,g=g)$loglik
    loglik.up  = ash(z-fitted.mode+0.01,1,g=g)$loglik
    loglik.posteriormean = ash(z-average.posteriormean,1,g=g)$loglik

    return(list(fitted.mode=fitted.mode, average.posteriormean =average.posteriormean,
         loglik = c(loglik,loglik.down,loglik.up,loglik.posteriormean)))
  }
  set.seed(100)
  z = rnorm(1000)+3
  check_mode(z,1,mixcompdist="uniform")
  check_mode(z,1,mixcompdist="normal")
  check_mode(z,1,mixcompdist="halfuniform")
```

@@

## Session information

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk-options, include=FALSE}
library(ashr)
source("chunk-options.R")
```

@@

I conjecture that the mean of the posterior means should be close to the
optimum for the mode... maybe even equal to it. (That is, this would constitute
a fixed point for the update. We aren't explicitly using that directly in the
current implementation; the uniform mixture uses `optim` to do it numerically;
the normal mixture uses a true EM I think...)

```{r}
check_mode = function(betahat, sebetahat, mixcompdist) {
  z.ash = ash(betahat,sebetahat,mixcompdist = mixcompdist,mode = "estimate")
  average.posteriormean = mean(get_pm(z.ash))
  fitted.mode = comp_mean(get_fitted_g(z.ash))[1]

  # Refit to get g.
  z.ash1 = ash(betahat - fitted.mode,sebetahat,mixcompdist = mixcompdist)
  g      = get_fitted_g(z.ash1)
  loglik = get_loglik(z.ash1)

  loglik.down          = ash(z - fitted.mode - 0.01,1,g = g)$loglik
  loglik.up            = ash(z - fitted.mode + 0.01,1,g = g)$loglik
  loglik.posteriormean = ash(z - average.posteriormean,1,g = g)$loglik

  return(list(fitted.mode = fitted.mode,
              average.posteriormean = average.posteriormean,
              loglik = c(loglik,loglik.down,loglik.up,loglik.posteriormean)))
}

set.seed(100)
z = rnorm(1000) + 3
print(check_mode(z,1,mixcompdist="uniform"))
print(check_mode(z,1,mixcompdist="normal"))
print(check_mode(z,1,mixcompdist="halfuniform"))
```

@@

## Session information.

### 2016-10-14 analysis/plot_lfsr.Rmd
remove pdf files
Encountered error in running 'ash' with REBayes package using stephens999/ashr with 'general' branch.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

```{r}
load("../output/dsc-shrink-files/res.RData")
source("../R/set_plot_colors.R")
library(dplyr)

@@

## Session information

```{r info}
sessionInfo()
```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk-options, include=FALSE}
library(dplyr)
library(ggplot2)
source("chunk-options.R")
```

TO DO: Add note here about having to first run script to generate data sets
required to run the analysis.

```{r}
load("../output/dsc-shrink-files/res.RData")
source("../R/set_plot_colors.R")

@@

## Session information.

```{r info}
print(sessionInfo())
```
